Using an Autoencoder Model to Characterize Air Pollution

### 2023-02-19 paper-draft/paper.tex
Maintenance commit

\begin{Center}
\begin{figure}[h!]
\caption{Data Pipeline}
\label{fig:pipeline}
    \begin{center}
    \includegraphics[width=10cm, height=13cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/pipeline.png}
    \end{center}
\end{figure}
\end{Center}

@@

% Correlation Matrix 
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/corr_matrix.png}
\end{center}
    \caption{Correlation Matrix for Carbon Monoxide (daily averages for cities throughout the US)}
\label{fig:matrix}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \caption{Unencoded R2 Scores}
    \label{fig:pipeline}
    \includegraphics[width=0.8\linewidth]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/unencoded_r2.png}
\end{figure}

@@

\begin{center}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth, height=7cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/pca_all_dims.png} 
    \caption{PCA Dimensionality Reduction}
    \label{fig:pca_dim_reduction}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth, height=7cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/pca_all_dims.png} 
    \caption{Autoencoder Dimensionality Reduction\ \note{Placeholder for AE}}
    \label{fig:ae_dim_reduction}
\end{figure}
\end{center}

@@

% co scatter
\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/region.png} 
    \caption{Model characterization grouped by region}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/outside-us.png}
    \caption{Model characterization of U.S. Territories}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/california.png} 
    \caption{Model characterization of California}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/texas.png} 
    \caption{Model characterization of Texas}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/new-york.png}
    \caption{Model characterization of New York}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/minnesota.png}
    \caption{Model characterization of Minnesota}
\end{subfigure}
\caption{Scatter plots of outlier and highly-populated cities over first two dimensions}
\label{fig:heuristic_labels}
\end{figure}

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\linewidth, height=10cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/population.png} 
    \caption{Model characterization grouped by region}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\linewidth, height=10cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/population_3and4.png}
    \caption{Model characterization of U.S. Territories}
\end{subfigure}
\caption{Scatter plots of outlier and highly-populated cities over first two dimensions}
\label{fig:population_comparison}
\end{figure}

@@

% Scattergeo 
\begin{figure}[h!]
    \caption{Geographic comparison of model embedding values versus daily pollution levels}
    \label{fig:outliers_vs_dense_cities}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/o3-dim1.png} 
    \caption{O3 values of the first encoded dimension (units of compression)}
    \label{fig:outliers}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/o3-first.png}
    \caption{O3 pollution values for the first day of data set ($\mu g/m^3$)}
    \label{fig:dense_cities}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/o3-dim2.png} 
    \caption{O3 values of the second encoded dimension (units of compression)}
    \label{fig:outliers}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/github_repos/Pollution-Autoencoders/paper-draft/images/o3-last.png}
    \caption{O3 pollution values for the last day of data set ($\mu g/m^3$)}
    \label{fig:dense_cities}
\end{subfigure}
\end{figure}

>>>>

\begin{Center}
\begin{figure}[h!]
\caption{Data Pipeline}
\label{fig:pipeline}
    \begin{center}
    \includegraphics[width=10cm, height=13cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/pipeline.png}
    \end{center}
\end{figure}
\end{Center}

@@

% Correlation Matrix 
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/corr_matrix.png}
\end{center}
    \caption{Correlation Matrix for Carbon Monoxide (daily averages for cities throughout the US)}
\label{fig:matrix}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \caption{Unencoded R2 Scores}
    \label{fig:pipeline}
    \includegraphics[width=0.8\linewidth]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/unencoded_r2.png}
\end{figure}

@@

\begin{center}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth, height=7cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/pca_all_dims.png} 
    \caption{PCA Dimensionality Reduction}
    \label{fig:pca_dim_reduction}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth, height=7cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/pca_all_dims.png} 
    \caption{Autoencoder Dimensionality Reduction\ \note{Placeholder for AE}}
    \label{fig:ae_dim_reduction}
\end{figure}
\end{center}

@@

% co scatter
\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/region.png} 
    \caption{Model characterization grouped by region}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/outside-us.png}
    \caption{Model characterization of U.S. Territories}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/california.png} 
    \caption{Model characterization of California}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/texas.png} 
    \caption{Model characterization of Texas}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/new-york.png}
    \caption{Model characterization of New York}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=0.8\linewidth, height=6cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/minnesota.png}
    \caption{Model characterization of Minnesota}
\end{subfigure}
\caption{Scatter plots of outlier and highly-populated cities over first two dimensions}
\label{fig:heuristic_labels}
\end{figure}

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\linewidth, height=10cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/population.png} 
    \caption{Model characterization grouped by region}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.0\linewidth, height=10cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/population_3and4.png}
    \caption{Model characterization of U.S. Territories}
\end{subfigure}
\caption{Scatter plots of outlier and highly-populated cities over first two dimensions}
\label{fig:population_comparison}
\end{figure}

@@

% Scattergeo 
\begin{figure}[h!]
    \caption{Geographic comparison of model embedding values versus daily pollution levels}
    \label{fig:outliers_vs_dense_cities}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/o3-dim1.png} 
    \caption{O3 values of the first encoded dimension (units of compression)}
    \label{fig:outliers}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/o3-first.png}
    \caption{O3 pollution values for the first day of data set ($\mu g/m^3$)}
    \label{fig:dense_cities}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/o3-dim2.png} 
    \caption{O3 values of the second encoded dimension (units of compression)}
    \label{fig:outliers}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth, height=8cm]{/home/nick/git/Pollution-Autoencoders/paper-draft/images/o3-last.png}
    \caption{O3 pollution values for the last day of data set ($\mu g/m^3$)}
    \label{fig:dense_cities}
\end{subfigure}
\end{figure}
